\begin{thebibliography}{45}
\bibitem{jegou2011pq}
H. J\'egou, M. Douze, and C. Schmid, ``Product quantization for nearest neighbor search,'' \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 33, no. 1, pp. 117--128, 2011.

\bibitem{malkov2020hnsw}
Y. A. Malkov and D. A. Yashunin, ``Efficient and robust approximate nearest neighbor search using hierarchical navigable small world graphs,'' \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 42, no. 4, pp. 824--836, 2020.

\bibitem{ootomo2024cagra}
K. Ootomo, A. Naruse, C. Nolet, R. Wang, T. Feh\'er, and Y. Wang, ``CAGRA: Highly parallel graph construction and approximate nearest neighbor search for GPUs,'' in \emph{Proc. 40th IEEE Int. Conf. Data Eng. (ICDE)}, 2024, pp. 4236--4247.

\bibitem{nvidia_cagraq}
C. J. Nolet, ``Accelerating vector search with RAPIDS RAFT,'' presented at the NeurIPS BigANN Workshop, 2023, slide deck. [Online]. Available: \url{https://big-ann-benchmarks.com/neurips23_slides/NVIDIA_Corey.pdf}.

\bibitem{subramanya2019diskann}
S. J. Subramanya, F. Devvrit, H. V. Simhadri, R. Krishnawamy, and R. Kadekodi, ``DiskANN: Fast accurate billion-point nearest neighbor search on a single node,'' in \emph{Advances in Neural Information Processing Systems}, vol. 32, 2019, pp. 13748--13758.

\bibitem{cuvs_wikiall}
NVIDIA RAPIDS cuVS, ``Wiki-all dataset,'' cuVS documentation. [Online]. Available: \url{https://docs.rapids.ai/api/cuvs/stable/cuvs_bench/wiki_all_dataset/} (accessed Jul. 17, 2026).

\bibitem{fatrq2026}
T. Zhang, F. Ponzina, and T. Rosing, ``FaTRQ: Tiered residual quantization for LLM vector search in far-memory-aware ANNS systems,'' in \emph{Proc. Design, Autom. \& Test Eur. Conf. (DATE)}, 2026, pp. 1--7.

\bibitem{yue2024rpq}
Q. Yue, X. Xu, Y. Wang, Y. Tao, and X. Luo, ``Routing-guided learned product quantization for graph-based approximate nearest neighbor search,'' in \emph{Proc. 40th IEEE Int. Conf. Data Eng. (ICDE)}, 2024, pp. 4870--4883.

\bibitem{tatsuno2024aisaq}
K. Tatsuno, D. Miyashita, T. Ikeda, K. Ishiyama, K. Sumiyoshi, and J. Deguchi, ``AiSAQ: All-in-storage ANNS with product quantization for DRAM-free information retrieval,'' arXiv preprint arXiv:2404.06004, 2024.

\bibitem{ivfrabitq2026}
J. Shi, J. Gao, J. Xia, T. B. Feh\'er, and C. Long, ``GPU-native approximate nearest neighbor search with IVF-RaBitQ: Fast index build and search,'' arXiv preprint arXiv:2602.23999, 2026.

\bibitem{kudo2025cccell}
K. Kudo, Y. Aiba, K. Hasegawa, X. Li, Y. Sano, and T. Sanuki, ``Energy-efficient in-memory computing using 3D Flash Memory with sequential multi-block activation and current control cell (CC cell),'' in \emph{Proc. IEEE Int. Memory Workshop (IMW)}, 2025, pp. 1--4.

\bibitem{kudo2026multilevel}
K. Kudo, Y. Aiba, K. Hasegawa, X. Li, Y. Sano, and T. Sanuki, ``Multi-level in-memory computing with 3D Flash Memory using activation-time-modulated sequential multi-block access and tightly integrated current control cell (CC cell),'' in \emph{Proc. IEEE Int. Memory Workshop (IMW)}, 2026, pp. 1--4.

\bibitem{indyk1998ann}
P. Indyk and R. Motwani, ``Approximate nearest neighbors: Towards removing the curse of dimensionality,'' in \emph{Proc. 30th Annu. ACM Symp. Theory Comput. (STOC)}, 1998, pp. 604--613.

\bibitem{datar2004lsh}
M. Datar, N. Immorlica, P. Indyk, and V. S. Mirrokni, ``Locality-sensitive hashing scheme based on p-stable distributions,'' in \emph{Proc. 20th Annu. Symp. Comput. Geom. (SoCG)}, 2004, pp. 253--262.

\bibitem{realm2020}
K. Guu, K. Lee, Z. Tung, P. Pasupat, and M.-W. Chang, ``Retrieval augmented language model pre-training,'' in \emph{Proc. 37th Int. Conf. Mach. Learn. (ICML)}, 2020, pp. 3929--3938.

\bibitem{dpr2020}
V. Karpukhin, B. O\u{g}uz, S. Min, P. Lewis, L. Wu, S. Edunov, D. Chen, and W.-T. Yih, ``Dense passage retrieval for open-domain question answering,'' in \emph{Proc. 2020 Conf. Empirical Methods Natural Lang. Process. (EMNLP)}, 2020, pp. 6769--6781.

\bibitem{rag2020}
P. Lewis, E. Perez, A. Piktus, F. Petroni, V. Karpukhin, N. Goyal, H. K\"uttler, M. Lewis, W.-T. Yih, T. Rockt\"aschel, S. Riedel, and D. Kiela, ``Retrieval-augmented generation for knowledge-intensive NLP tasks,'' in \emph{Advances in Neural Information Processing Systems}, vol. 33, 2020, pp. 9459--9474.

\bibitem{colbert2020}
O. Khattab and M. Zaharia, ``ColBERT: Efficient and effective passage search via contextualized late interaction over BERT,'' in \emph{Proc. 43rd Int. ACM SIGIR Conf. Res. Develop. Inf. Retrieval}, 2020, pp. 39--48.

\bibitem{ge2013opq}
T. Ge, K. He, Q. Ke, and J. Sun, ``Optimized product quantization for approximate nearest neighbor search,'' in \emph{Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2013, pp. 2946--2953.

\bibitem{babenko2012imi}
A. Babenko and V. Lempitsky, ``The inverted multi-index,'' in \emph{Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2012, pp. 3069--3076.

\bibitem{babenko2014aq}
A. Babenko and V. Lempitsky, ``Additive quantization for extreme vector compression,'' in \emph{Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2014, pp. 931--938.

\bibitem{kalantidis2014lopq}
Y. Kalantidis and Y. Avrithis, ``Locally optimized product quantization for approximate nearest neighbor search,'' in \emph{Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2014, pp. 2321--2328.

\bibitem{andre2021quickeradc}
F. Andr\'e, A.-M. Kermarrec, and N. Le Scouarnec, ``Quicker ADC: Unlocking the hidden potential of product quantization with SIMD,'' \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 43, no. 5, pp. 1666--1677, 2021.

\bibitem{johnson2021faiss}
J. Johnson, M. Douze, and H. J\'egou, ``Billion-scale similarity search with GPUs,'' \emph{IEEE Transactions on Big Data}, vol. 7, no. 3, pp. 535--547, 2021.

\bibitem{guo2020scann}
R. Guo, P. Sun, E. Lindgren, Q. Geng, D. Simcha, F. Chern, and S. Kumar, ``Accelerating large-scale inference with anisotropic vector quantization,'' in \emph{Proc. 37th Int. Conf. Mach. Learn. (ICML)}, 2020, pp. 3887--3896.

\bibitem{gao2024rabitq}
J. Gao and C. Long, ``RaBitQ: Quantizing high-dimensional vectors with a theoretical error bound for approximate nearest neighbor search,'' \emph{Proceedings of the ACM on Management of Data}, vol. 2, no. 3, Art. no. 167, 27 pages, 2024.

\bibitem{chen2021spann}
Q. Chen, B. Zhao, H. Wang, M. Li, C. Liu, Z. Li, M. Yang, and J. Wang, ``SPANN: Highly-efficient billion-scale approximate nearest neighborhood search,'' in \emph{Advances in Neural Information Processing Systems}, vol. 34, 2021, pp. 5199--5212.

\bibitem{tian2024smartanns}
B. Tian, H. Liu, Z. Duan, X. Liao, H. Jin, and Y. Zhang, ``Scalable billion-point approximate nearest neighbor search using SmartSSDs,'' in \emph{Proc. 2024 USENIX Annu. Tech. Conf. (USENIX ATC)}, 2024, pp. 1135--1150.

\bibitem{wang2024ndsearch}
Y. Wang, S. Li, Q. Zheng, L. Song, Z. Li, A. Chang, H. Li, and Y. Chen, ``NDSearch: Accelerating graph-traversal-based approximate nearest neighbor search through near data processing,'' in \emph{Proc. 51st Annu. IEEE/ACM Int. Symp. Comput. Archit. (ISCA)}, 2024, pp. 368--381.

\bibitem{xu2023proxima}
W. Xu, J. Chen, P.-K. Hsu, J. Kang, M. Zhou, S. Pinge, S. Yu, and T. Rosing, ``Proxima: Near-storage acceleration for graph-based approximate nearest neighbor search in 3D NAND,'' \emph{IEEE Transactions on Computers}, vol. 75, no. 6, pp. 2114--2127, 2026.

\bibitem{ikeda2025storage_nn}
T. Ikeda, D. Miyashita, and J. Deguchi, ``On storage neural network augmented approximate nearest neighbor search,'' arXiv preprint arXiv:2501.16375, 2025.

\bibitem{zandieh2025turboquant}
A. Zandieh, M. Daliri, M. Hadian, and V. Mirrokni, ``TurboQuant: Online vector quantization with near-optimal distortion rate,'' in \emph{Proc. 14th Int. Conf. Learn. Representations (ICLR)}, 2026.

\bibitem{han2025polarquant}
I. Han, P. Kacham, A. Karbasi, V. Mirrokni, and A. Zandieh, ``PolarQuant: Quantizing KV caches with polar transformation,'' arXiv preprint arXiv:2502.02617, 2025.

\bibitem{jacques2013qjl}
L. Jacques, ``A quantized Johnson--Lindenstrauss lemma: The finding of Buffon's needle,'' \emph{IEEE Transactions on Information Theory}, vol. 61, no. 9, pp. 5012--5027, 2015.

\bibitem{liu2024kivi}
Z. Liu, J. Yuan, H. Jin, S. Zhong, Z. Xu, V. Braverman, B. Chen, and X. Hu, ``KIVI: A tuning-free asymmetric 2bit quantization for KV cache,'' in \emph{Proc. 41st Int. Conf. Mach. Learn. (ICML)}, 2024, pp. 32332--32344.

\bibitem{liu2024cachegen}
Y. Liu, H. Li, Y. Cheng, S. Ray, Y. Huang, Q. Zhang, K. Du, J. Yao, S. Lu, G. Ananthanarayanan, M. Maire, H. Hoffmann, A. Holtzman, and J. Jiang, ``CacheGen: KV cache compression and streaming for fast large language model serving,'' in \emph{Proc. ACM SIGCOMM 2024 Conf.}, 2024, pp. 38--56.

\bibitem{lukken2021computational_storage}
C. Lukken and A. Trivedi, ``Past, present and future of computational storage: A survey,'' arXiv preprint arXiv:2112.09691, 2021.

\bibitem{singh2019near_memory}
G. Singh, L. Chelini, S. Corda, A. J. Awan, S. Stuijk, R. Jordans, H. Corporaal, and A.-J. Boonstra, ``Near-memory computing: Past, present, and future,'' \emph{Microprocessors and Microsystems}, vol. 71, Art. no. 102868, 2019.

\bibitem{hyun2024pathfinding}
B. Hyun, T. Kim, D. Lee, and M. Rhu, ``Pathfinding future PIM architectures by demystifying a commercial PIM technology,'' in \emph{Proc. 30th IEEE Int. Symp. High-Perform. Comput. Archit. (HPCA)}, 2024, pp. 263--279.

\bibitem{oliveira2024mimdram}
G. F. Oliveira, A. Olgun, A. G. Yaglikci, F. N. Bostanci, J. G\'omez-Luna, S. Ghose, and O. Mutlu, ``MIMDRAM: An end-to-end processing-using-DRAM system for high-throughput, energy-efficient and programmer-transparent multiple-instruction multiple-data computing,'' in \emph{Proc. 30th IEEE Int. Symp. High-Perform. Comput. Archit. (HPCA)}, 2024, pp. 186--203.

\bibitem{seo2025facil}
S. H. Seo, J. Kim, D. Lee, S. Yoo, S. Moon, Y. Park, and J. W. Lee, ``FACIL: Flexible DRAM address mapping for SoC-PIM cooperative on-device LLM inference,'' in \emph{Proc. 31st IEEE Int. Symp. High-Perform. Comput. Archit. (HPCA)}, 2025, pp. 1720--1733.

\bibitem{kim2025crossbit}
H. Kim, S. Song, S. Choi, J. Choe, S. Han, J. Park, J. Lee, and J.-J. Kim, ``CrossBit: Bitwise computing in NAND flash memory with inter-bitline data communication,'' in \emph{Proc. 58th IEEE/ACM Int. Symp. Microarchitecture (MICRO)}, 2025, pp. 1193--1206.

\bibitem{gouk2024dockerssd}
D. Gouk, M. Kwon, H. Bae, and M. Jung, ``DockerSSD: Containerized in-storage processing and hardware acceleration for computational SSDs,'' in \emph{Proc. 30th IEEE Int. Symp. High-Perform. Comput. Archit. (HPCA)}, 2024, pp. 379--394.

\bibitem{hu2022imc3dnand}
H.-W. Hu, W.-C. Wang, C. K. Chen, Y.-C. Lee, B.-R. Lin, H.-M. Wang, Y.-P. Lin, Y.-C. Lin, C.-C. Hsieh, C.-M. Hu, Y.-T. Lai, H.-S. Chen, Y.-H. Chang, H.-P. Li, T.-W. Kuo, K.-C. Wang, M.-F. Chang, C.-H. Hung, and C.-Y. Lu, ``A 512Gb in-memory-computing 3D-NAND flash supporting similar-vector-matching operations on edge-AI devices,'' in \emph{Proc. IEEE Int. Solid-State Circuits Conf. (ISSCC)}, 2022, pp. 138--140.

\bibitem{hu2022ice}
H.-W. Hu, W.-C. Wang, Y.-H. Chang, Y.-C. Lee, B.-R. Lin, H.-M. Wang, Y.-P. Lin, Y.-M. Huang, C.-Y. Lee, T.-H. Su, C.-C. Hsieh, C.-M. Hu, Y.-T. Lai, C. K. Chen, H.-S. Chen, H.-P. Li, T.-W. Kuo, M.-F. Chang, K.-C. Wang, C.-H. Hung, and C.-Y. Lu, ``ICE: An intelligent cognition engine with 3D NAND-based in-memory computing for vector similarity search acceleration,'' in \emph{Proc. 55th IEEE/ACM Int. Symp. Microarchitecture (MICRO)}, 2022, pp. 763--783.
\end{thebibliography}
